---
title: "Prototype KPI-script: Absolute GHG Accounting"
author: "Gerrit Versteeg"
date: "March 31th, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Absolute GHG Accounting
This KPI-script calculates

## Four models

## Overview steps in script

# Data Processing
## Setting up the environment

***
IN/OUTPUT

| In/Out | Filename   |  Size | Description |
|:------|:------------------|----:|:------------------------------|
| Input | CustFac_General.csv | 247/18 | |
| Input | IC_Corporate.csv | 48/7 | |
| Input | IC_ProjFin.csv | 59/6 | |
| Input | IC_FinInst.csv | 101/23 | |
| Input | IC_PrivEq.csv | 39/43 | |
| Input | PEF_Investments.csv | 117/5 | |
| Input | PEF_RegionPerc.csv | 18/3 | |
| Input | Fctr_EcEmis.csv | 23/17 | |
| Input | Fctr_CapInt.csv | 23/17 | |
| Input | Fctr_CBbrkdwn.csv | 23/17 | |
| Input | Fctr_Out2Elec.csv | 23/17 | |
| LUT | MAP_CntrReg.csv | 87/2 | |
| LUT | MAP_SctrMdl.csv | 21/2 | |
| LUT | MAP_ICSctrMdl.csv | 18/2 | |

***

```{r setup_env,ECHO = TRUE}
library("tidyverse", warn.conflicts=FALSE)      ## load tidyverse silently

## Source micro-services
## 1. contains all microservices for first KPI
source("microservices/uS_microservices.R")

## Setup locations
rawdir <- "datalake/raw_data/"
lutdir <- "datalake/luts/"
clndir <- "datalake/clean_data/"
valdir <- "datalake/valid_data/"
inddir <- "datalake/indicators/"
dptdir <- "datalake/data_points/"
laydir <- "datalake/infoproducts/GIS_layers/"
qlkdir <- "datalake/infoproducts/Qlik_cubes/"
sopdir <- "datalake/infoproducts/sopact_sheets/"

## Setup parameters
version <- ""
indate = "2019-03-31"
lutdate = "2019-03-31"
outdate = "2019-03-31"

## Setup filenames
fname_in_custG <- paste0(clndir,"CustFac_General", "_", outdate,".csv")
fname_in_ICCp <- paste0(clndir,"IC_Corporate", "_", outdate,".csv")
fname_in_ICPF <- paste0(clndir,"IC_ProjFin", "_", outdate,".csv")
fname_in_ICFI <- paste0(clndir,"IC_FinInst", "_", outdate,".csv")
fname_in_ICPE <- paste0(clndir,"IC_PrivEq", "_", outdate,".csv")
fname_in_PEFInv <- paste0(clndir,"PEF_Investments", "_", outdate,".csv")
fname_in_PEFReg <- paste0(clndir,"PEF_RegionPerc", "_", outdate,".csv")
fname_in_EcEF <- paste0(clndir,"Fctr_EcEmis", "_", outdate,".csv")
fname_in_CpIF <- paste0(clndir,"Fctr_CapInt", "_", outdate,".csv")
fname_in_CBBD <- paste0(clndir,"Fctr_CBbrkdwn", "_", outdate,".csv")
fname_in_OutElc <- paste0(clndir,"Fctr_Out2Elec", "_", outdate,".csv")
fname_lut_Map_CntrReg <- paste0(lutdir,"Map_CntrReg", "_", outdate,".csv")
fname_lut_Map_SctrMdl <- paste0(lutdir,"Map_SctrMdl", "_", outdate,".csv")
fname_lut_Map_ICSctrMdl <- paste0(lutdir,"Map_ICSctrMdl", "_", outdate,".csv")
fname_out <- paste0(inddir,"KPI_AbsGHGAcc", "_", outdate,".csv")

```

## Prive Equity Fund Preparation
### Determining Investment Percentages per Country
Calculate investment percentage per PEF-customer per country

```{r 1.PEF-InvPct, ECHO = TRUE}
PEFInv <- read.csv2(fname_in_PEFInv, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFReg <- read.csv2(fname_in_PEFReg, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFInvPct <- uS001_PE_InvPct(investments = PEFInv,
                             contracted = PEFReg)
head(PEFInvPct, 5)
```

