---
title: "KPI_Gender"
author: "G. Versteeg"
date: "4/9/2019"
output: pdf_document
---

# Gender Accounting
## In short
This script calculates some of the indicators used in FMO Gender Data (based on Impact Card Data). It is created to show R's ease and speed-of-use.
Relevant notes:

1. Only active accounts/clients included
2. All data is reported by clients
3. No data available on board composition
4. No check for double counting if co-investing
5. Data not attributed to FMO's investments 
6. Impact tab entries as '0' included in the # of clients that reported on gender data while only the entries that were empty are counted as 'Not Reported'. 


## Basis of data used
The script uses the data available in the Excel-sheet "Gender Indicators.xlsx", dd. April 7th, 2019 provided by Guilia Debernardini.


```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r environment, include=FALSE, warning=FALSE}
library(tidyverse)

## Setup locations
insite <- ""
rawdir <- "datalake/raw_data/"
lutdir <- "datalake/luts/"
clndir <- "datalake/clean_data/"
valdir <- "datalake/valid_data/"
inddir <- "datalake/indicators/"
dptdir <- "datalake/data_points/"
laydir <- "datalake/infoproducts/GIS_layers/"
qlkdir <- "datalake/infoproducts/Qlik_cubes/"
sopdir <- "datalake/infoproducts/sopact_sheets/"

## Setup parameters
version <- ""
indate = "2019-04-07"
lutdate = ""
outdate = "2019-04-07"

## Setup filenames
fname_in_custPF <- paste0(clndir,"CustPortfolio", "_", outdate,".csv")
fname_in_icGen <- paste0(clndir,"IC_General", "_", outdate,".csv")
fname_in_GenInd <- paste0(clndir,"GenderIndicators", "_", outdate,".csv")
```

# Portfolio - Direct Investments (incl. FI, AGRI, EN, PE)

## Indicators for "Coverage rate" (no. of clients)
Total number of clients versus number of client reporting on female employment

```{r ind_1, echo=TRUE, warning=FALSE}
GenInd <- read.csv2(fname_in_GenInd,
                    stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
df <- GenInd %>%
  filter(Active_Inactive_account != "NOT ACTIVE") %>%
  filter(Impact_Card_Type != "Private Equity Fund")
Ind_NoCustTotal <- length(unique(df$Customer_Number))

df <- df %>%
  filter(nr_Direct_Employment_operations_and_maintainence_for_women != "Not Reported")
Ind_NoCustRepFem <- length(unique(df$Customer_Number))
Ind_CoverageRate <- Ind_NoCustRepFem / Ind_NoCustTotal
round(Ind_CoverageRate*100,2)
```


## Indicators "Gender employment in Operations & Maintenance"
Number of (total/female) jobs reported by all clients

```{r ind_a, echo=TRUE, warning=FALSE}
Ind_NoJobsTotal <- 
  sum(as.numeric(GenInd$Direct_employment_Operations_Maintenance_nr), na.rm = TRUE)
icGen <- read.csv2(fname_in_icGen,
                    stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
IQ <- "Direct employment (operations & maintenance) for women"
df <- icGen %>%
  filter(Impact_Question == IQ) %>%
  filter(Active_Non_Active != "NOT ACTIVE") %>%
  filter(Impact_Card_Type != "Private Equity Fund") %>%
  group_by(Customer_Name) %>%
  slice(1) %>%
  ungroup
Ind_NoJobsFem <- sum(as.numeric(df$Answer), na.rm = TRUE)
Ind_PcJobsFem <- Ind_NoJobsFem / Ind_NoJobsTotal
round(Ind_PcJobsFem*100,2)
```

## Indicators "Gender employment in Operations & Maintenance (for clients reporting on female employment)"
Number of (total/female) jobs reported by clients reporting on female employment

```{r ind_g, echo=TRUE, warning=FALSE}
df <- GenInd %>%
  filter(Female_Employment_Reported_Not_Reported_by_Client != "Not Reported") %>%
  filter(Active_Inactive_account != "NOT ACTIVE") %>%
  filter(!is.na(Active_Inactive_account)) %>%
  filter(Impact_Card_Type != "Private Equity Fund")
Ind_NoJobsR <- sum(as.numeric(df$Direct_employment_Operations_Maintenance_nr),
                      na.rm = TRUE)
Ind_PcJobsFemR <- Ind_NoJobsFem / Ind_NoJobsR
round(Ind_PcJobsFemR*100,2)
```

## Indicator "Avg. female employment per client"
Average female employment per client for clients reporting on female employment

```{r ind_i, echo=TRUE, warning=FALSE}
Ind_AvgNoJobsFemPerCustR <- Ind_NoJobsFem / Ind_NoCustRepFem
round(Ind_AvgNoJobsFemPerCustR,0)
```

# Results

```{r setup result, echo=FALSE, warning=FALSE}
result <- data.frame(Indicator = character(0),
                     Datapoint = character(0),
                     Number = numeric(0),
                     Perc = numeric(0),
                     stringsAsFactors = FALSE)

i <- 1
if(exists("Ind_NoCustTotal")) {
  result[i,] <- NA
  result$Indicator[i] <- "Number of clients"
  result$Datapoint[i] <- "Total"
  result$Number[i] <- round(Ind_NoCustTotal,0)
  result$Perc[i] <- NA
  i <- i + 1
}

if(exists("Ind_NoCustRepFem") & exists("Ind_CoverageRate")) {
  result[i,] <- NA
  result$Indicator[i] <- ""
  result$Datapoint[i] <- "Reporting direct female employment"
  result$Number[i] <- round(Ind_NoCustRepFem,0)
  result$Perc[i] <- paste0(round(Ind_CoverageRate*100,0), " %")
  i <- i + 1
}

if(exists("Ind_NoJobsTotal")) {
  result[i,] <- NA
  result$Indicator[i] <- "Portfolio (all clients)"
  result$Datapoint[i] <- "Total employment"
  result$Number[i] <- round(Ind_NoJobsTotal,0)
  result$Perc[i] <- NA
  i <- i + 1
}

if(exists("Ind_NoJobsFem") & exists("Ind_PcJobsFem")) {
  result[i,] <- NA
  result$Indicator[i] <- ""
  result$Datapoint[i] <- "Female employment"
  result$Number[i] <- round(Ind_NoJobsFem,0)
  result$Perc[i] <- paste0(round(Ind_PcJobsFem*100,0), " %")
  i <- i + 1
}

if(exists("Ind_NoJobsR")) {
  result[i,] <- NA
  result$Indicator[i] <- "Portfolio (clients reporting female employment)"
  result$Datapoint[i] <- "Total employment"
  result$Number[i] <- round(Ind_NoJobsR,0)
  result$Perc[i] <- NA
  i <- i + 1
}

if(exists("Ind_NoJobsFem") & exists("Ind_PcJobsFemR")) {
  result[i,] <- NA
  result$Indicator[i] <- ""
  result$Datapoint[i] <- "Female employment"
  result$Number[i] <- round(Ind_NoJobsFem,0)
  result$Perc[i] <- paste0(round(Ind_PcJobsFemR*100,0), " %")
  i <- i + 1
}

if(exists("Ind_AvgNoJobsFemPerCustR")) {
  result[i,] <- NA
  result$Indicator[i] <- ""
  result$Datapoint[i] <- "Avg. female employment per client"
  result$Number[i] <- round(Ind_AvgNoJobsFemPerCustR,0)
  result$Perc[i] <- NA
  i <- i + 1
}
```

```{r show_result, echo=FALSE, results="asis"}
options(knitr.kable.NA = "")
kable(result, row.names = FALSE, 
      caption="FMO Gender Indicators (Direct Investments)",
      format.args = list(decimal.mark = ',', big.mark = '.'))
```

