---
title: "Prototype KPI-script: Absolute GHG Accounting"
author: "Gerrit Versteeg"
date: "March 31th, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Absolute GHG Accounting
## In short
This script calculates the absolute greenhouse gas emission for all customers of FMO. The GHG-accounting model is based on the FMO Impact Model methodology as described in general in: "FMO Impact Model - methodology document 25 March 2019.pdf".

The calculations used are described in more detail in FMO's technical paper, version 2, October 2018 ("Absolute GHG Accounting Approach.pdf"").

## Four models
Four calculation models are used, sequenced below in prefered usage:

* model 1. use verified, actual GHG emissions (ISO 14064)
* model 2. use primary physical activity data to estimate GHG emission
* model 3. use primary economic activity data to estimate GHG emission
* model 4. use portfolio data to estimate GHG emission

## Explaining Scope 1, 2 & 3
To help delineate direct and indirect emission sources, improve transparency, and provide utility for different types of organizations and different types of climate policies and business goals, three “scopes” (scope 1, scope 2, and scope 3) are defined for GHG accounting and reporting purposes. Scopes 1 and 2 are carefully defined in this standard to ensure that two or more companies will not account for emissions in the same scope. This makes the scopes amenable for use in GHG programs where double counting matters. Companies shall separately account for and report on scopes 1 and 2 at a minimum.

#### Scope 1: Direct GHG Emissions
Direct GHG emissions occur from sources that are owned or controlled by the company, for example, emissions from combustion in owned or controlled boilers, furnaces, vehicles, etc.; emissions from chemical production in owned or controlled process equipment. Direct CO2 emissions from the combustion of biomass shall not be included in scope 1 but reported separately. GHG emissions not covered by the Kyoto Protocol, e.g. CFCs, NOx, etc. shall not be included in scope 1 but may be reported separately.

#### Scope 2: Electricity Indirect GHG Emissions
Scope 2 accounts for GHG emissions from the generation of purchased electricity consumed by a company. Purchased electricity is defined as electricity that is purchased or otherwise brought into the organizational boundary of the company. Scope 2 emissions physically occur at the facility where electricity is generated.

#### Scope 3: Other Indirect GHG Emissions
Scope 3 is an optional reporting category that allows for the treatment of all other indirect emissions. Scope 3 emissions are a consequence of the activities of the company, but occur from sources not owned or controlled by the company. Some examples of scope 3 activities are extraction and production of purchased materials; transportation of purchased fuels; and use of products and services.

## Overview steps in script

# Data Processing
## Setting up the environment

***
IN/OUTPUT

| In/Out | Filename   |  Size | Description |
|:------|:------------------|----:|:------------------------------|
| Input | CustFac_General.csv | 247/18 | |
| Input | IC_Corporate.csv | 48/7 | |
| Input | IC_ProjFin.csv | 59/6 | |
| Input | IC_FinInst.csv | 101/23 | |
| Input | IC_PrivEq.csv | 39/43 | |
| Input | PEF_Investments.csv | 117/5 | |
| Input | PEF_RegionPerc.csv | 18/3 | |
| Input | Fctr_EcEmis1.csv | 23/19 | |
| Input | Fctr_EcEmis2.csv | 23/19 | |
| Input | Fctr_CapInt.csv | 23/19 | |
| Input | Fctr_CBbrkdwn.csv | 23/17 | |
| Input | Fctr_Out2Elec.csv | 23/17 | |
| LUT | MAP_CntrReg.csv | 87/2 | |
| LUT | MAP_SctrMdl.csv | 21/2 | |
| LUT | MAP_ICSctrMdl.csv | 18/2 | |
| Output | KPI_aGHG.csv | 23/17 | |

***

```{r setup_env, echo=FALSE, warning=FALSE}
## Load packages used
library("tidyverse", warn.conflicts=FALSE)

## Source micro-services
source("microservices/uS005_AbsEms_Corp.R")
source("microservices/uS006_AbsEms_PrFin.R")
source("microservices/uS007_AbsEms_PrEq2.R")
source("microservices/uS008_AbsEms_FI.R")

## Setup locations in data lake
rawdir <- "datalake/raw_data/"
lutdir <- "datalake/luts/"
clndir <- "datalake/clean_data/"
valdir <- "datalake/valid_data/"
inddir <- "datalake/indicators/"
dptdir <- "datalake/data_points/"
laydir <- "datalake/infoproducts/GIS_layers/"
qlkdir <- "datalake/infoproducts/Qlik_cubes/"
sopdir <- "datalake/infoproducts/sopact_sheets/"

## Setup times and version parameters
indate = "2019-04-11"
lutdate = "2019-04-11"
outdate = "2019-04-11"
version <- ""

## Setup filenames
fname_in_custG <- paste0(clndir,"Cust_General", "_", outdate,".csv")
fname_in_ICCp <- paste0(clndir,"IC_Corporate", "_", outdate,".csv")
fname_in_ICPF <- paste0(clndir,"IC_ProjFin", "_", outdate,".csv")
fname_in_ICFI <- paste0(clndir,"IC_FinInst", "_", outdate,".csv")
fname_in_ICPE <- paste0(clndir,"IC_PrivEq", "_", outdate,".csv")
fname_in_EcEF1 <- paste0(clndir,"Fctr_EcEmis1", "_", outdate,".csv")
fname_in_EcEF2 <- paste0(clndir,"Fctr_EcEmis2", "_", outdate,".csv")
fname_in_CpIF <- paste0(clndir,"Fctr_CapInt", "_", outdate,".csv")
fname_in_CBBD <- paste0(clndir,"Fctr_CBbrkdwn", "_", outdate,".csv")

fname_in_lutC <- paste0(lutdir,"Map_CntrReg", "_", outdate,".csv")
fname_in_lutS <- paste0(lutdir,"Map_SctrMdl", "_", outdate,".csv")
fname_in_lutICS <- paste0(lutdir,"Map_ICSctrMdl", "_", outdate,".csv")

fname_in_PEFConsPKfctrs <- paste0(dptdir,"PEF_ConsPKF", "_", outdate,".csv")
fname_in_PEFConsEC1fctrs <- paste0(dptdir,"PEF_ConsECF1", "_", outdate,".csv")
fname_in_PEFConsEC2fctrs <- paste0(dptdir,"PEF_ConsECF2", "_", outdate,".csv")
fname_in_PEFConsSize <- paste0(dptdir,"PEF_ConsSize", "_", outdate,".csv")
fname_in_PEFConsSctrs <- paste0(dptdir,"PEF_ConsSctrs", "_", outdate,".csv")

fname_out_AE_Corp1 <- paste0(inddir,"KPI_aGHG_Corp1", "_", outdate,".csv")
fname_out_AE_Corp2 <- paste0(inddir,"KPI_aGHG_Corp2", "_", outdate,".csv")
fname_out_AE_PrFin1 <- paste0(inddir,"KPI_aGHG_PrFin1", "_", outdate,".csv")
fname_out_AE_PrFin2 <- paste0(inddir,"KPI_aGHG_PrFin2", "_", outdate,".csv")
fname_out_AE_PrEq1 <- paste0(inddir,"KPI_aGHG_PrEq1", "_", outdate,".csv")
fname_out_AE_PrEq2 <- paste0(inddir,"KPI_aGHG_PrEq2", "_", outdate,".csv")
fname_out_AE_FI1 <- paste0(inddir,"KPI_aGHG_FI1", "_", outdate,".csv")
fname_out_AE_FI2 <- paste0(inddir,"KPI_aGHG_FI2", "_", outdate,".csv")
fname_out_AE <- paste0(inddir,"KPI_aGHG", "_", outdate,".csv")

```


## General customers
### Determining customer types

```{r 1.PEF-InvPct, echo=FALSE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
table(custG$IC_Type)
```

## Calculate Absolute Emissions

### Corporates (scope 1)

Calculate absolute emissions (Scope 1) for each Corporate customer.

```{r 2.AbsEms-Corp1, echo=TRUE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
custG <- custG[custG$IC_Type == "corporate",]
ICCp <- read.csv2(fname_in_ICCp, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
EcEF <- read.csv2(fname_in_EcEF1, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
CpIF <- read.csv2(fname_in_CpIF, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
lutC <- read.csv2(fname_in_lutC, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
lutS <- read.csv2(fname_in_lutS, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)

AE_Corp1 <- uS005_AbsEms_Corp(impactcard = ICCp,
                             customers = custG,
                             factors = EcEF,
                             PKF = CpIF,
                             scope = 1,
                             countrymap = lutC,
                             sectormap = lutS)
write.csv2(AE_Corp1, file = fname_out_AE_Corp1, row.names = FALSE,
           fileEncoding = "UTF-8")

head(AE_Corp1, 10)
```

### Corporates (scope 2)

Calculate absolute emissions (Scope 2) for each Corporate customer.

```{r 3.AbsEms-Corp2, echo=FALSE}
EcEF <- read.csv2(fname_in_EcEF2, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)

AE_Corp2 <- uS005_AbsEms_Corp(impactcard = ICCp,
                             customers = custG,
                             factors = EcEF,
                             PKF = CpIF,
                             scope = 2,
                             countrymap = lutC,
                             sectormap = lutS)
write.csv2(AE_Corp2, file = fname_out_AE_Corp2, row.names = FALSE,
           fileEncoding = "UTF-8")

table(AE_Corp2$method)
```

### Project-Finances (scope 1)

Calculate absolute emissions (Scope 1) for each project finance customer.

```{r 4.AbsEms-PF1, echo=FALSE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
custG <- custG[custG$IC_Type == "project finance",]
ICPF <- read.csv2(fname_in_ICPF, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)
EcEF <- read.csv2(fname_in_EcEF1, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)

AE_PrFin1 <- uS006_AbsEms_PrFin(impactcard = ICPF,
                             customers = custG,
                             factors = EcEF,
                             scope = 1,
                             countrymap = lutC,
                             sectormap = lutS)

write.csv2(AE_PrFin1, file = fname_out_AE_PrFin1, row.names = FALSE,
           fileEncoding = "UTF-8")

hist(AE_PrFin1$abs_ems, main = "Histogram of Emissions",
     xlab = "Absolute emissions")
```

### Project-Finances (scope 2)

Calculate absolute emissions (Scope 2) for each project finance customer.

```{r 5.AbsEms-PF2, echo=FALSE}
EcEF <- read.csv2(fname_in_EcEF2, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8", check.names = FALSE)

AE_PrFin2 <- uS006_AbsEms_PrFin(impactcard = ICPF,
                             customers = custG,
                             factors = EcEF,
                             scope = 2,
                             countrymap = lutC,
                             sectormap = lutS)

write.csv2(AE_PrFin2, file = fname_out_AE_PrFin2, row.names = FALSE,
           fileEncoding = "UTF-8")

sum(AE_PrFin2$abs_ems, na.rm = TRUE)
```

### Private Equity Funds (scope 1)

Calculate absolute emissions (scope 1) for each Private Equity Fund customer.

```{r 6.AbsEms-PE1, echo=FALSE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                   fileEncoding = "UTF-8", check.names = FALSE)
custG <- custG[custG$IC_Type == "private equity fund",]
lutICS <- read.csv2(fname_in_lutICS, stringsAsFactors = FALSE,
                   fileEncoding = "UTF-8", check.names = FALSE)
PEFConsECF <- read.csv2(fname_in_PEFConsEC1fctrs, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)
PEFConsPKF <- read.csv2(fname_in_PEFConsPKfctrs, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)
EcEF <- read.csv2(fname_in_EcEF1, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)
CpIF <- read.csv2(fname_in_CpIF, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)
PEFConsSize <- read.csv2(fname_in_PEFConsSize, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)
PEFConsSctrs <- read.csv2(fname_in_PEFConsSctrs, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)

AE_PrEq1 <- uS007_AbsEms_PrEq2(customers = custG,
                            c_ecfactors = PEFConsECF,
                            c_pkfactors = PEFConsPKF,
                            ECF = EcEF,
                            PKF = CpIF,
                            sizes = PEFConsSize,
                            sectors = PEFConsSctrs,
                            costPK_msme = 1.19852941176471,
                            costPK_corp = 0.727941176470588,
                            sectormap = lutICS)

write.csv2(AE_PrEq1, file = fname_out_AE_PrEq1, row.names = FALSE,
           fileEncoding = "UTF-8")

head(AE_PrEq1, 5)
```
### Private Equity Funds (scope 2)

Calculate absolute emissions (scope 2) for each Private Equity Fund customer.

```{r 6.AbsEms-PE2, echo=FALSE}
PEFConsEC2fctrs <- read.csv2(fname_in_PEFConsEC2fctrs, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)
EcEF <- read.csv2(fname_in_EcEF2, 
                           stringsAsFactors = FALSE, fileEncoding = "UTF-8",
                           check.names = FALSE)

AE_PrEq2 <- uS007_AbsEms_PrEq2(customers = custG,
                            c_ecfactors = PEFConsECF,
                            c_pkfactors = PEFConsPKF,
                            ECF = EcEF,
                            PKF = CpIF,
                            sizes = PEFConsSize,
                            sectors = PEFConsSctrs,
                            costPK_msme = 1.19852941176471,
                            costPK_corp = 0.727941176470588,
                            sectormap = lutICS)

write.csv2(AE_PrEq2, file = fname_out_AE_PrEq1, row.names = FALSE,
           fileEncoding = "UTF-8")

head(AE_PrEq2, 5)
```

### Financial Institutions (scope 1)

Calculate absolute emissions (scope 1) for each Financial Institution.

```{r 7.AbsEms-FI1, echo=FALSE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                   fileEncoding = "UTF-8", check.names = FALSE)
custG <- custG[custG$IC_Type == "financial institution",]
EcEF <- read.csv2(fname_in_EcEF1, stringsAsFactors = FALSE,
                                  fileEncoding = "UTF-8", check.names = FALSE)
CpIF <- read.csv2(fname_in_CpIF, stringsAsFactors = FALSE,
                                 fileEncoding = "UTF-8", check.names = FALSE)
ICFI <- read.csv2(fname_in_ICFI, stringsAsFactors = FALSE, 
                                 fileEncoding = "UTF-8", check.names = FALSE)
lutICS <- read.csv2(fname_in_lutICS, stringsAsFactors = FALSE,
                                     fileEncoding = "UTF-8", check.names = FALSE)
lutC <- read.csv2(fname_in_lutC, stringsAsFactors = FALSE,
                                     fileEncoding = "UTF-8", check.names = FALSE)

# AE_FI1 <- uS008_AbsEms_FI(customers = custG,
#                            ecfactors = EcEF,
#                            pkfactors = CpIF,
#                            impactcard = ICFI,
#                            costPK_msme = 1.19852941176471,
#                            costPK_corp = 0.727941176470588,
#                            countrymap = lutC,
#                            sectormap = lutICS)

#write.csv2(AE_FI1, file = fname_out_AE_FI1, row.names = FALSE,
#           fileEncoding = "UTF-8")

#head(AE_FI1, 5)
```

### Financial Institutions (scope 2)

Calculate absolute emissions (scope 2) for each Financial Institution.

```{r 8.AbsEms-FI2, echo=FALSE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                   fileEncoding = "UTF-8", check.names = FALSE)
custG <- custG[custG$IC_type == "financial institution",]
EcEF <- read.csv2(fname_in_EcEF2, stringsAsFactors = FALSE,
                                  fileEncoding = "UTF-8", check.names = FALSE)

#AE_FI2 <- uS008_AbsEms_FI(customers = custG,
#                            ecfactors = EcEF,
#                            pkfactors = CpIF,
#                            impactcard = ICFI,
#                            costPK_msme = 1.19852941176471,
#                            costPK_corp = 0.727941176470588,
#                            countrymap = lutC,
#                            sectormap = lutICS)

#write.csv2(AE_FI2, file = fname_out_AE_FI2, row.names = FALSE,
#           fileEncoding = "UTF-8")

#head(AE_FI2, 5)
```

## Results

### Table of emissions per department
Combine all absolute emissions datapoints and for each customer add the Net Portfolio and the relevant department.

```{r 9.Results 1, echo=FALSE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                   fileEncoding = "UTF-8", check.names = FALSE)

colnames(AE_Corp1) <- paste0(colnames(AE_Corp1),"_1")
colnames(AE_Corp2) <- paste0(colnames(AE_Corp2),"_2")
#colnames(AE_FI1) <- paste0(colnames(AE_FI1),"_1")
#colnames(AE_FI2) <- paste0(colnames(AE_FI2),"_2")
colnames(AE_PrEq1) <- paste0(colnames(AE_PrEq1),"_1")
colnames(AE_PrEq2) <- paste0(colnames(AE_PrEq2),"_2")
colnames(AE_PrFin1) <- paste0(colnames(AE_PrFin1),"_1")
colnames(AE_PrFin2) <- paste0(colnames(AE_PrFin2),"_2")
AE <- rbind(cbind(AE_Corp1, AE_Corp2),
#            cbind(AE_FI1, AE_FI2),
            cbind(AE_PrEq1, AE_PrEq2),
            cbind(AE_PrFin1, AE_PrFin2))
AE <- select(AE, c(1,2,5,6))
colnames(AE)[1] <- "Customer_ID"
colnames(AE)[2] <- "Scope_1"
colnames(AE)[3] <- "Scope_2"
colnames(AE)[4] <- "Method"
AE <- mutate(AE, Dep = NA, NetPort = NA)
for (i in c(1:nrow(AE))) {
  curcust <- AE$Customer_ID[i]
  AE$Dep[i] <- custG$Department[custG$Customer_ID == curcust]
  NetPort <- custG$Net_portfolio[custG$Customer_ID == curcust]
  if(!(is.na(NetPort))) {
    NetPort <- ifelse(NetPort < 0, 0, NetPort)
  }
  AE$NetPort[i] <- NetPort
  AE <- mutate(AE, Ems = (Scope_1 + Scope_2))
}
write.csv2(AE, file = fname_out_AE, row.names = FALSE,
         fileEncoding = "UTF-8")

AEsum <- AE %>%
  group_by(Dep) %>%
  summarise(Scope_1 = sum(Scope_1, na.rm = TRUE), 
            Scope_2 = sum(Scope_2, na.rm = TRUE),
            AbsEms = sum(Ems, na.rm = TRUE), 
            Inv = sum(NetPort, na.rm = TRUE)) %>%
  mutate(GHGpMEur = (AbsEms / (Inv / 10^6)))

AEsum
```

### Show stacked bar chart of emissions per scope within departments

Show the absolute emissions for each scope per department in a stacked bar chart.

```{r 10.Stacked bar, echo=TRUE}

dfG1 <- AEsum %>%
  select(-Inv, -GHGpMEur, -AbsEms) %>%
  mutate(Scope_1 = (Scope_1/10^3), Scope_2 = (Scope_2/10^3)) %>% 
  gather(key = "scope", value = "ems", -Dep, na.rm = TRUE)

G1 <- ggplot() + geom_bar(aes(y = ems, x = Dep, fill = scope), 
                          data = dfG1, stat="identity") +
                          labs(x="Department", y="Absolute Emissions") +
                          theme(axis.text.x = element_text(angle = -50, 
                                                           hjust = 0,
                                                           vjust = 1))
G1
```


