---
title: "KPI_Gender"
author: "G. Versteeg"
date: "4/9/2019"
output: pdf_document
---

# Gender Accounting
## In short
This script calculates some of the indicators used in FMO Gender Data (based on Impact Card Data). It is meant to show R's ease-of-use.

## Basis of data used
The script uses the data available in the Excel-sheet "Gender Indicators.xlsx", dd. April 7th, 2019 provided by Guilia Debernardini.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r environment, include=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)

## Setup locations
insite <- ""
rawdir <- "datalake/raw_data/"
lutdir <- "datalake/luts/"
clndir <- "datalake/clean_data/"
valdir <- "datalake/valid_data/"
inddir <- "datalake/indicators/"
dptdir <- "datalake/data_points/"
laydir <- "datalake/infoproducts/GIS_layers/"
qlkdir <- "datalake/infoproducts/Qlik_cubes/"
sopdir <- "datalake/infoproducts/sopact_sheets/"

## Setup parameters
version <- ""
indate = "2019-04-07"
lutdate = ""
outdate = "2019-04-07"

## Setup filenames
fname_in_custPF <- paste0(clndir,"CustPortfolio", "_", outdate,".csv")
fname_in_icGen <- paste0(clndir,"IC_General", "_", outdate,".csv")
fname_in_GenInd <- paste0(clndir,"GenderIndicators", "_", outdate,".csv")
```

# Portfolio

## Direct Investments (incl. FI, AGRI, EN, PE)

### ABC: Indicatoren "Percentage % Female Employment"
```{r ind_a, echo=TRUE, warning=FALSE}
GenInd <- read.csv2(fname_in_GenInd,
                    stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
Ind_A <- as.numeric(GenInd$Direct_employment_Operations_Maintenance_nr)

icGen <- read.csv2(fname_in_icGen,
                    stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
IQ <- "Direct employment (operations & maintenance) for women"
df <- icGen %>%
  filter(Impact_Question == IQ) %>%
  filter(Active_Non_Active != "NOT ACTIVE") %>%
  filter(Impact_Card_Type != "Private Equity Fund") %>%
  group_by(Customer_Name) %>%
  slice(1) %>%
  ungroup
Ind_B <- sum(as.numeric(df$Answer), na.rm = TRUE)

Ind_C <- Ind_B/Ind_A
Ind_C
```

### DEF: Indicatoren "Coverage rate"

```{r ind_d, echo=TRUE, warning=FALSE}
df <- GenInd %>%
  filter(Active_Inactive_account != "NOT ACTIVE") %>%
  filter(Impact_Card_Type != "Private Equity Fund")
Ind_D <- length(unique(df$Customer_Number))

df <- df %>%
  filter(nr_Direct_Employment_operations_and_maintainence_for_women != "Not Reported")
Ind_E <- length(unique(df$Customer_Number))

Ind_F <- Ind_E/Ind_D
```

### G: Indicator "# Total Direct Employment (for clients that reported on female employment)"

```{r ind_g, echo=TRUE, warning=FALSE}
df <- GenInd %>%
  filter(Female_Employment_Reported_Not_Reported_by_Client != "Not Reported") %>%
  filter(Active_Inactive_account != "NOT ACTIVE") %>%
  filter(!is.na(Active_Inactive_account)) %>%
  filter(Impact_Card_Type != "Private Equity Fund")
v <- as.numeric(df$Direct_employment_Operations_Maintenance_nr)
Ind_G <- sum(v, na.rm = TRUE)
Ind_G
```

### H: Indicator "% Female Employment (for clients that reported on female employment)"

```{r ind_h, echo=TRUE, warning=FALSE}
Ind_H <- Ind_B/Ind_G
Ind_H
```

### I: Indicator "Avg. per client (for clients that reported on female employment)"

```{r ind_i, echo=TRUE, warning=FALSE}
Ind_I <- Ind_B/Ind_E
Ind_I
```

## Results

```{r setup result, echo=FALSE, warning=FALSE}
result <- data.frame(Indicator = character(0),
                     Datapoint = character(0),
                     DirectInv = numeric(0),
                     Perc = numeric(0),
                     stringsAsFactors = FALSE)

i <- 1
result[i,] <- NA
result$Indicator[i] <- "Number of clients"
result$Datapoint[i] <- "Total"
result$DirectInv[i] <- round(Ind_D,0)
result$Perc[i] <- NA

i <- 2
result[i,] <- NA
result$Indicator[i] <- ""
result$Datapoint[i] <- "Reporting direct female employment"
result$DirectInv[i] <- round(Ind_E,0)
result$Perc[i] <- paste0(round(Ind_F*100,0), " %")

i <- 3
result[i,] <- "---"

i <- 4
result[i,] <- NA
result$Indicator[i] <- "Portfolio (all clients)"
result$Datapoint[i] <- "# Direct employment"
result$DirectInv[i] <- round(Ind_A,0)
result$Perc[i] <- NA

i <- 5
result[i,] <- NA
result$Indicator[i] <- ""
result$Datapoint[i] <- "# Direct female employment"
result$DirectInv[i] <- round(Ind_B,0)
result$Perc[i] <- paste0(round(Ind_C*100,0), " %")

i <- 6
result[i,] <- "---"

i <- 7
result[i,] <- NA
result$Indicator[i] <- "Portfolio (clients reporting female employment)"
result$Datapoint[i] <- "# Direct employment"
result$DirectInv[i] <- round(Ind_G,0)
result$Perc[i] <- NA

i <- 8
result[i,] <- NA
result$Indicator[i] <- ""
result$Datapoint[i] <- "# Direct female employment"
result$DirectInv[i] <- round(Ind_B,0)
result$Perc[i] <- paste0(round(Ind_H*100,0), " %")

i <- 9
result[i,] <- NA
result$Indicator[i] <- ""
result$Datapoint[i] <- "Avg. female employment per client"
result$DirectInv[i] <- round(Ind_I,0)
result$Perc[i] <- NA
```


```{r show result, echo=TRUE, warning=FALSE}
options(knitr.kable.NA = "")
kable(result[-c(3,6),], caption="FMO Gender Indicators",
      row.names = FALSE)
```

