---
title: "Prototype KPI-script: Consolidate Private Equity Funds"
author: "Gerrit Versteeg"
date: "March 31th, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Absolute GHG Accounting
## In short
This KPI-script consolidates investments in Private Equity Funds for each customer.

## Overview steps in script

  1. Determine investment percentages per country
  2. Consolidate investment percentage to PK-factors (Cap.Int)
  3. Consolidate investment percentage to economic factors scope 2
  3. Consolidate investment percentage to economic factors scope 1
  4. Consolidate investment percentage towards size (MSME, Corp)
  5. Consolidate investment percentage towards impact card sector

# Data Processing
## Setting up the environment

***
IN/OUTPUT

| In/Out | Filename   |  Size | Description |
|:------|:------------------|----:|:------------------------------|
| Input | CustFac_General.csv | 247/18 | |
| Input | IC_Corporate.csv | 48/7 | |
| Input | IC_ProjFin.csv | 59/6 | |
| Input | IC_FinInst.csv | 101/23 | |
| Input | IC_PrivEq.csv | 39/43 | |
| Input | PEF_Investments.csv | 117/5 | |
| Input | PEF_RegionPerc.csv | 18/3 | |
| Input | Fctr_EcEmis1.csv | 23/19 | |
| Input | Fctr_EcEmis2.csv | 23/19 | |
| Input | Fctr_CapInt.csv | 23/19 | |
| Input | Fctr_CBbrkdwn.csv | 23/17 | |
| Input | Fctr_Out2Elec.csv | 23/17 | |
| LUT | MAP_CntrReg.csv | 87/2 | |
| LUT | MAP_SctrMdl.csv | 21/2 | |
| LUT | MAP_ICSctrMdl.csv | 18/2 | |
| Output | PEF_InvPct | 18/2 | |
| Output | PEF_ConsPKF | 18/2 | |
| Output | PEF_ConsECF1 | 18/2 | |
| Output | PEF_ConsECF2 | 18/2 | |
| Output | PEF_ConsSize | 18/2 | |
| Output | PEF_ConsSctrs | 18/2 | |

***

```{r setup_env,ECHO = TRUE}
library("tidyverse", warn.conflicts=FALSE)      ## load tidyverse silently

## Source micro-services
## 1. contains all microservices for first KPI
source("microservices/uS001_PE_InvPct.R")
source("microservices/uS002_PE_ConsolidateFactors.R")
source("microservices/uS003_PE_ConsolidateSectors.R")
source("microservices/uS004_PE_ConsolidateSize.R")

## Setup locations
rawdir <- "datalake/raw_data/"
lutdir <- "datalake/luts/"
clndir <- "datalake/clean_data/"
valdir <- "datalake/valid_data/"
inddir <- "datalake/indicators/"
dptdir <- "datalake/data_points/"
laydir <- "datalake/infoproducts/GIS_layers/"
qlkdir <- "datalake/infoproducts/Qlik_cubes/"
sopdir <- "datalake/infoproducts/sopact_sheets/"

## Setup parameters
version <- ""
indate = "2019-03-31"
lutdate = "2019-03-31"
outdate = "2019-03-31"

## Setup filenames
fname_in_custG <- paste0(clndir,"CustFac_General", "_", outdate,".csv")
fname_in_ICPE <- paste0(clndir,"IC_PrivEq", "_", outdate,".csv")
fname_in_PEFInv <- paste0(clndir,"PEF_Investments", "_", outdate,".csv")
fname_in_PEFReg <- paste0(clndir,"PEF_RegionPerc", "_", outdate,".csv")
fname_in_EcEF1 <- paste0(clndir,"Fctr_EcEmis1", "_", outdate,".csv")
fname_in_EcEF2 <- paste0(clndir,"Fctr_EcEmis2", "_", outdate,".csv")
fname_in_CpIF <- paste0(clndir,"Fctr_CapInt", "_", outdate,".csv")
fname_in_lutC <- paste0(lutdir,"Map_CntrReg", "_", outdate,".csv")
fname_out_PEFInvPct <- paste0(dptdir,"PEF_InvPct", "_", outdate,".csv")
fname_out_PEFConsPKfctrs <- paste0(dptdir,"PEF_ConsPKF", "_", outdate,".csv")
fname_out_PEFConsEC1fctrs <- paste0(dptdir,"PEF_ConsECF1", "_", outdate,".csv")
fname_out_PEFConsEC2fctrs <- paste0(dptdir,"PEF_ConsECF2", "_", outdate,".csv")
fname_out_PEFConsSize <- paste0(dptdir,"PEF_ConsSize", "_", outdate,".csv")
fname_out_PEFConsSctrs <- paste0(dptdir,"PEF_ConsSctrs", "_", outdate,".csv")

```


## General customers
### Listing the customer types

```{r 1.PEF-CustList, ECHO = TRUE}
custG <- read.csv2(fname_in_custG, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
table(custG$IC_type)
```


## Prive Equity Fund Preparation

### Determining Investment Percentages per Country

Calculate investment percentages per Private Equity Fund for each customer seperated into GHG-countries.

```{r 1.PEF-InvPct, ECHO = TRUE}
PEFInv <- read.csv2(fname_in_PEFInv, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFReg <- read.csv2(fname_in_PEFReg, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
lutC <- read.csv2(fname_in_lutC, stringsAsFactors = FALSE,
                   fileEncoding = "UTF-8")
PEFInvPct <- uS001_PE_InvPct(investments = PEFInv,
                             contracted = PEFReg,
                             countrymap = lutC)
write.csv2(PEFInvPct, file = fname_out_PEFInvPct, row.names = FALSE,
           fileEncoding = "UTF-8")
head(PEFInvPct, 5)
```

### Consolidating PK-Factors (Cap.Intensity)
Consolidate Capital Intensity Factors (GHG-country/sector) per customer

```{r 2.PEF-ConsPKFct, ECHO = TRUE}
CpIF <- read.csv2(fname_in_CpIF, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFConsPKF <- uS002_PE_ConsolidateFactors(invperc = PEFInvPct,
                             factors = CpIF,
                             countrymap <- lutC)
write.csv2(PEFConsPKF, file = fname_out_PEFConsPKfctrs, row.names = FALSE,
           fileEncoding = "UTF-8")
head(PEFConsPKF, 5)
```

### Consolidating EcEF - scope 2
Consolidate emission fators (scope 2) per customer

```{r 3.PEF-ConsEc2Fct, ECHO = TRUE}
EcEF2 <- read.csv2(fname_in_EcEF2, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFConsECF2 <- uS002_PE_ConsolidateFactors(invperc = PEFInvPct,
                             factors = EcEF2,
                             countrymap <- lutC)
write.csv2(PEFConsECF2, file = fname_out_PEFConsEC2fctrs, 
           row.names = FALSE, fileEncoding = "UTF-8")
head(PEFConsECF2, 5)
```

### Consolidating EcEF - scope 1
Consolidate emission fators (scope 1) per customer

```{r 4.PEF-ConsEc1Fct, ECHO = TRUE}
EcEF1 <- read.csv2(fname_in_EcEF1, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFConsECF1 <- uS002_PE_ConsolidateFactors(invperc = PEFInvPct,
                             factors = EcEF1,
                             countrymap <- lutC)
write.csv2(PEFConsECF1, file = fname_out_PEFConsEC1fctrs, 
           row.names = FALSE, fileEncoding = "UTF-8")
head(PEFConsECF1, 5)
```

### Consolidate IC-Sectors per PEF-customer
Calculate the PEF-investments (or contracted if not present) for each PEF-customer for each Impact Card Sector

```{r 5.PEF-ConsSect, ECHO = TRUE}
ICPE <- read.csv2(fname_in_ICPE, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFInv <- read.csv2(fname_in_PEFInv, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFConsSctrs <- uS003_PE_ConsolidateSectors(investments = PEFInv,
                             contracted = ICPE)
write.csv2(PEFConsSctrs, file = fname_out_PEFConsSctrs, 
           row.names = FALSE, fileEncoding = "UTF-8")
head(PEFConsSctrs, 5)
```

### Consolidate investments towards size per PEF-customer
Calculate the PEF-investments (or contracted if not present) for each PEF-customer for each size (SME versus Corporate)

```{r 6.PEF-ConsSect, ECHO = TRUE}
ICPE <- read.csv2(fname_in_ICPE, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")
PEFInv <- read.csv2(fname_in_PEFInv, stringsAsFactors = FALSE,
                    fileEncoding = "UTF-8")

PEFConsSize <- uS004_PE_ConsolidateSize(investments = PEFInv,
                             contracted = ICPE)

write.csv2(PEFConsSize, file = fname_out_PEFConsSize, 
           row.names = FALSE, fileEncoding = "UTF-8")
head(PEFConsSize, 5)
```

